A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
Writing + more benchmarks

We attempted to measure the 
See Figure ~\ref{fig:tables}
 \begin{figure}[H]
   \centering
   \includegraphics[width=4in]{tables.pdf}
   \caption{}
   \label{fig:tables}
 \end{figure}

>>>>

For simple tabulation hashing with variable length strings, we decided to use a
fixed number of tables $N$ and round robin between them for every byte.  We
found the optimal value of $N$ to be 8 experimentally.  We limited our choices
to powers of 2 so that costly modulo operations could be avoided by using bit
masks Figure ~\ref{fig:tables} shows the performance of different numbers of
tabulation tables.  Eight turned out to be the sweetspot
 \begin{figure}[H]
   \centering
   \includegraphics[width=4in]{tables.pdf}
   \caption{6000000 keys}
   \label{fig:tables}
 \end{figure}
